\section{How does Covered work?}\label{page_howitworks}
 To begin extracting coverage numbers for a design, the design must first be simulated with VCD style dumping turned on for the modules undergoing coverage analysis. Once a VCD file has been created, the design must be parsed by the Covered utility, and a database file must be created, storing the parsed information. This is achieved through the use of Covered's score command. Once an initial database file has been generated, Covered will read in the specified  VCD file along with the initial database file and update the database file to contain the coverage results extracted from the dumpfile. This step also occurs during Covered's score command phase. Once the database file contains scoring information, several things can occur with that database file.

 First, a user may create coverage reports from the scored database file. Several types of reports can be generated from a given scored database file. The following types of reports can be generated (this is not intended to be a complete list):\begin{enumerate}
\item 
Summarized reports: only coverage percentages are reported for modules/module instances. These types of reports are typically generated first to get a high-level view of the coverage amount.\item 
Verbose reports: detailed information on certain coverage results are displayed, including Verilog code snippets and detailed analysis reports on logical values.\item 
Module instance reports: look at summary/verbose reports for each individual module instance in the analyzed design.\item 
Module reports: look at summary/verbose reports for a module (combines all analyzed module instances of the specified module).\end{enumerate}


 Second, a user may merge coverage databases for the same design (but from different simulation runs). This is necessary since one test will usually not test an entire design. Typically, a test suite  (containing more than one diagnostic) is used to test a design. By merging the coverage results of all test runs, we can generate coverage reports that reflect the amount of the design covered by the entire test suite (rather than just a single test). Any database file that was generated from the exact same design may be merged; however, merging different designs is prohibited by Covered and will produce an error to the user (without affecting any of the specified design files).

